---
title: "Autocorrelation in Group Size"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)

## Global options
opts_knit$set(root.dir = normalizePath(here::here()))
opts_chunk$set(fig.path = 'plots/',
               fig.height = 8,
               fig.width = 12,
	             cache = TRUE,
               tidy = FALSE,
               message = FALSE,
               warning = FALSE)
read_chunk('scripts/group-size-autocorr.R')
```

## Set up environment

```{r set-up-env, message = FALSE, echo = TRUE, results = 'hide'}
```

## Obtain data from babase

*This will not work with "live" babase data until you have set up a connection between R and babase!* 

This entails getting a papio login, and creating an ssh tunnel from your computer to papio in putty (Windows) or terminal (Mac/Unix).

## Creating the connections

On my machine, I type something like this into terminal to make the ssh tunnel:

`ssh -f fac13@papio.biology.duke.edu -L 2222:localhost:5432 -N`

You wil obviously need to change the username before the @ symbol. If you get that sorted out, you can create a connection to babase using the code below. These lines create _connections_ to babase tables and then pull data into R. It doesn't actually collect any data until the very end so that database backend does the heavy lifting. In this approach, you're essentially specifying joins among your table connections, sending the query to the database to execute, and collecting the result.

Alternatively, you can write a query in SQL, run it in babase, output to csv, and load that into R into a variable called "kids".

```{r database-connections-hidden, echo=FALSE}
```

```{r database-connections-general, eval=FALSE}
```

## Experienced group size

In this section, we find the group size that each individual female experienced on each "monthly birthday" throughout her life.

Steps:

1. Find all live-born females born into study population
2. Create sequence of 1-month time steps for each female from date of birth until her last "monthly birthday" before death.
3. Obtain total group size for the female on each date from the members table

### Create age sequences

```{r find-kids}
```

### Match to group sizes

```{r match-grp-size}
```

### Plot of experienced group size.

```{r plot_experienced_group_size}
```

<br>
<br>

## Autocorrelation

In this section, we apply an autocorrelation function to each individual female's experienced group size over her life. We're going to average this across individuals of different birth group sizes.

If, for example, being born in a small group is a reliable signal that the adult social environment is likely to be a large group 10 years latter, that would appear as negative autocorrelation at lag 10 years.

### Apply ACF to individuals

```{r group-size-acf}
```

### Plot of individual ACF

```{r plot-group-size-acf}
```

